\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{parskip} % Gestione automatica dello spazio tra paragrafi
\pagenumbering{gobble} % Rimuove la numerazione delle pagine
\setlength{\parindent}{0pt} % Disattiva l'indentazione dei paragrafi

% Adjust space between sections and subsections
\titlespacing*{\section}{0pt}{6pt}{6pt}
\titlespacing*{\subsection}{0pt}{4pt}{4pt}

\raggedbottom % Evita di riempire forzatamente la pagina

\begin{document}
\thispagestyle{empty} % Nessuna numerazione o intestazione nella prima pagina

% Start of the two-column layout
\noindent
\begin{minipage}[t]{0.25\textwidth}
    % Left side content
    \vspace{0.3cm}
    { \LARGE  \textbf{Lattaruolo \\[0.1cm] Andrea}} \\
    
    { \LARGE \textbf{\textcolor{orange}{\newline Software \\[0.1cm] developer}}} \\   
    \section*{}
    \rule{0.6cm}{0.3mm}
    \section*{Experience}
    \vspace{6.7cm} % Ridotto lo spazio riservato per Experience
    \rule{0.6cm}{0.3mm}
    \section*{Personal projects}
    \vspace{2.8cm} % Ridotto lo spazio per Personal Projects
    \rule{0.6cm}{0.3mm}
    \section*{Education}
    \vspace{4cm} % Ridotto lo spazio per Education
    \rule{0.6cm}{0.3mm}
\end{minipage}
\hfill
\begin{minipage}[t]{0.75\textwidth}
    \rule{\linewidth}{0.5mm} % Riduci questo spazio per evitare che tutto scorra su un'altra pagina
    \subsection*{Contacts}
    \begin{itemize}[leftmargin=1cm]
        \item Email: lattaruolo.96@gmail.com
        %\item Cellphone: +39 3489937013
    \end{itemize}
    \rule{\linewidth}{0.5mm}
    \\[0.1cm]
    Genuinely understanding of problems during a software development process and ability to find solutions to them. With a background of solo and team developing. \\[0.3cm]
    Proficient in Python, Angular and Flutter \\[0.1cm]
    Good in Java, Typescript, Html, Css, SQL, Firebase, Github, Docker

    \rule{\linewidth}{0.5mm}
    \subsection*{Fondazione Bruno Kessler/ Software developer - Full stack}
    \textit{ March 2020 - Present, Trento Italy  } \\
    \begin{itemize}[leftmargin=1cm]
        \item Developed a windows application for satellite image downloading and transformation using Python and Ionic (back-end and front-end).
        \item Docker image creation for satellite image downloading and transformation.
        \item LLM research how to use them using Llama models and HuggingFace models.
        \item Front end development of a console using Angular.
        \item Decomposing a software application in different microservices using Java Springboot.
    \end{itemize}
    \vspace{0.2cm} % Riduci lo spazio qui se necessario
    \subsection*{Edith Group /Software developer - Back end}
    \textit{January 2020 - March 2020, Udine Italy} \\
    \begin{itemize}[leftmargin=1cm]
        \item C\# debugging and testing on applications.
        \item SQL queries scripting.
    \end{itemize}
    \rule{\linewidth}{0.5mm}
    \subsection*{Khamilia / Flutter app - Google Firebase }
    \textit{June 2024 - Ongoing, Trento, Italy} \\
    \begin{itemize}[leftmargin=1cm]
        \item Khamilia is your journal personal assistant improving quality of life
        \item Developed during the Gemini API Developer Competition
    \end{itemize}
    \subsection*{Leetcode / Daily problems solving }
    \textit{June 2024 - Ongoing, Trento, Italy} \\
    \begin{itemize}[leftmargin=1cm]
        \item Proficient in easy and medium problems
    \end{itemize}
    \rule{\linewidth}{0.5mm}
    \subsection*{University of Udine / Master degree - Algorithms and automatic reasoning }
    \textit{December 2018 - December 2020, Udine, Italy} \\
    \begin{itemize}[leftmargin=1cm]
        \item Abroad study at Griffith university \textit{May 2019 - November 2019, Gold Coast, Australia} 
        \item B2 certifications IELTS to attend to the Australian university
    \end{itemize}

    \subsection*{University of Udine / Bachelor degree - Computer science }
    \textit{September 2015 - December 2019, Udine, Italy} \\
    \rule{\linewidth}{0.5mm}
    
\end{minipage}

\end{document}
